Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-09 article.tex
organization of the paper

	This paper is organized as follows.

%	The permutation pattern problem asks if there exists a normalized subsequence of a text $\ptext$ which equals to a motif $\pmotif$.
%	If so we write $\pmotif \preceq \ptext$.
%	If not we say that $\ptext$ \textbf{avoid} $\pmotif$.
%	This was first introduced by Knuth \cite{Knuth:1997:ACP:260999}
%	who proves that permutation sortable by stacks
%	avoid the motif $231$.
%	The problem is NP-hard in general,
%	but for some classes of permutation,
%	polynomial time solution exists.
%	For instance the separable permutation \cite{Bose93patternmatching}.
%	We contribute studying this problem
%	and related one for the class of permutation avoiding (231,213).
%	This is interesting because this class is in linear bijection between the classes of (123,132),(132,213) and (132,213)
%	avoiding permutation, and all the classes obtainable by reversal or/and
%	complementation (see \cite{Simion1985383}).\\
%
%
%
%	This paper is organized as follows.
%	Section 2 presents the needed definition.
%	Section 3 solves the permutation pattern problem with
%	(213,231) avoiding permutations.
%	Section 4 focus on the problem the
%	related problem of computing a longest permutation avoiding (213,231).
%	Finally, section 5 summarizes
%	results for related problems.

@@

\end{itemize}

\end{proof}

@@

\section{Longest Subsequence Avoiding \\(231,213) Common for Two Permutation}

>>>>

	This paper is organized as follows.
	In Section~\ref{section:Definitions} the needed definition are presented.
	Section~\ref{section:both are (231,213)-avoiding} is devoted to presenting 
	an online linear-time algorithm in case both the pattern and the target
	permutation are $(213,231)$-avoiding,
	where Section~\ref{section:sigma only avoid 231 and 213} focuses on the case
	where the pattern only is $(213,231)$-avoiding.
	In Section~\ref{section:bivincular} we give a polynomial-time algorithm
	for $(213,231)$-avoiding bivincular patterns.
	In Section~\ref{section:LCS} we consider the problem of finding the longest
	$(213,231)$-avoiding pattern in a permutation.
	In Section~\ref{section:LCS common 2 permutations} we give a
	polynomial-time algorithm for computing the longest 
	$(213,231)$-avoiding pattern common to two permutations.

@@

\end{itemize}
\end{proof}

@@

\section{Longest Subsequence Avoiding \\(231,213) Common for Two Permutation}
\label{section:LCS common 2 permutations}
